---
title: "Bayesian Imputation for Daily New Infections in North Carolina "
author: "Cindy J. Pang"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: yeti
    highlight: zenburn

---
## COVID-19 Incidence Backcasting 
The following code utilizes the backcasting method from [Phipps, Grafton, and Kompas (2020)](https://royalsocietypublishing.org/doi/10.1098/rsos.200909#d1e2162)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#### S"ET DIR
setwd("C:\\Users\\Cindy Pang\\mcmc-dummy")
#### LOAD LIBRARIES
library(dplyr)
library(readr)
library(tidyr)
library(ggplot2)
library(knitr)

#### READ IN DATA
nc_data <- read_csv("Data//JHU_NC_Daily.csv")

#### AGGREGATE DATA TO STATE-LEVEL 
nc_data <- nc_data %>%
  group_by(Date)%>%
  summarize(state_cases = sum(daily_cases), 
            state_deaths = sum(daily_deaths))

```
### Set-Up Time Lag as Gamma Distribution 
Let's assume that the time from infection($t'$) to death ($t$) $t-t'$ follows a Gamma distribution with $\alpha = (\frac{\mu}{\sigma})^2$ and $\beta = \frac{\sigma^2}{\mu}$ where $\mu$ is the time from infection to death and $\sigma$ is the standard deviation. [Linton et al.](https://www.mdpi.com/2077-0383/9/2/538) fitted a Gamma distribution to case data and found an mean incubation period of 6 days with a 95% Credible Interval of 12.8-17.5 days and obtained a mean estimate of onset from symptoms to death of 15.0 days with 95% Credible Interval of 12.8-17.5 days.
```{r Gamma Set-Up}
### Set Up Variables, units are in days
mean.incubation = 6.0
mean.symp.to.death = 15.0

std.incubation = mean(12.8, 17.5)
std.symp.to.death = mean(12.8, 17.5)

mu = mean.incubation + mean.symp.to.death
sigma = std.incubation + std.symp.to.death

alpha = (mu/sigma)^2
beta = sigma^2/mu
```
Using these literature values, we have a $\mu$ =`r mu`, $\sigma$ = `r sigma`, $\alpha$ = `r alpha`, and $\beta$ = `r beta`.  

Let's set up the Gamma Distribution
```{r Gamma MCMC}
set.seed(7)

inf.to.death <- rgamma(n = 10000, shape = alpha, scale = beta)
hist(inf.to.death, xlab = "Days", main = "Time from Infections to Death")
summary(inf.to.death)
```